---
title: "NucleotideDiversity"
output: html_document
date: "2024-02-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}

mlf.indels.500 <- read_tsv("mlf.BNC2buffered.withindels.500window.windowed.pi")
mlf.indels.1k <- read_tsv("mlf.BNC2buffered.withindels.1kwindow.windowed.pi")
mlf.indels.10k <- read_tsv("mlf.BNC2buffered.withindels.10kwindow.windowed.pi")

flf.indels.500 <- read_tsv("flf.BNC2buffered.withindels.500window.windowed.pi")
flf.indels.1k <- read_tsv("flf.BNC2buffered.withindels.1kwindow.windowed.pi")
flf.indels.10k <- read_tsv("flf.BNC2buffered.withindels.10kwindow.windowed.pi")

mlf.noindels.20 <- read_tsv("mlf.BNC2buffered.NOindels.20window.windowed.pi")
mlf.noindels.100 <- read_tsv("mlf.BNC2buffered.NOindels.100window.windowed.pi")
mlf.noindels.200 <- read_tsv("mlf.BNC2buffered.NOindels.200window.windowed.pi")
mlf.noindels.500 <- read_tsv("mlf.BNC2buffered.NOindels.500window.windowed.pi")
mlf.noindels.1k <- read_tsv("mlf.BNC2buffered.NOindels.1kwindow.windowed.pi")
mlf.noindels.10k <- read_tsv("mlf.BNC2buffered.NOindels.10kwindow.windowed.pi")

flf.noindels.20 <- read_tsv("flf.BNC2buffered.NOindels.20window.windowed.pi")
flf.noindels.100 <- read_tsv("flf.BNC2buffered.NOindels.100window.windowed.pi")
flf.noindels.200 <- read_tsv("flf.BNC2buffered.NOindels.200window.windowed.pi")
flf.noindels.500 <- read_tsv("flf.BNC2buffered.NOindels.500window.windowed.pi")
flf.noindels.1k <- read_tsv("flf.BNC2buffered.NOindels.1kwindow.windowed.pi")
flf.noindels.10k <- read_tsv("flf.BNC2buffered.NOindels.10kwindow.windowed.pi")

fems.noindels.500 <- read_tsv("females.BNC2buffered.NOindels.500window.windowed.pi")
fems.noindels.1k <- read_tsv("females.BNC2buffered.NOindels.1kwindow.windowed.pi")
fems.noindels.10k <- read_tsv("females.BNC2buffered.NOindels.10kwindow.windowed.pi")

all.indels.500 <- read_tsv("all.BNC2buffered.withindels.500window.windowed.pi")
all.indels.1k <- read_tsv("all.BNC2buffered.withindels.1kwindow.windowed.pi")
all.indels.10k <- read_tsv("all.BNC2buffered.withindels.10kwindow.windowed.pi")

all.noindels.20 <- read_tsv("all.BNC2buffered.NOindels.20window.windowed.pi")
all.noindels.100 <- read_tsv("all.BNC2buffered.NOindels.100window.windowed.pi")
all.noindels.200 <- read_tsv("all.BNC2buffered.NOindels.200window.windowed.pi")
all.noindels.500 <- read_tsv("all.BNC2buffered.NOindels.500window.windowed.pi")
all.noindels.1k <- read_tsv("all.BNC2buffered.NOindels.1kwindow.windowed.pi")
all.noindels.10k <- read_tsv("all.BNC2buffered.NOindels.10kwindow.windowed.pi")

tajD.indels.100 <- read_tsv("BNC2.tajimasd.allinds.100.Tajima.D")
tajD.indels.200 <- read_tsv("BNC2.tajimasd.allinds.200.Tajima.D")
tajD.indels.1k <- read_tsv("BNC2.tajimasd.allinds.1k.Tajima.D")
tajD.indels.10k <- read_tsv("BNC2.tajimasd.allinds.10k.Tajima.D")

tajD.noindels.100 <- read_tsv("all.BNC2buffered.tajimasd.allinds.noindels.100.Tajima.D")
tajD.noindels.500 <- read_tsv("all.BNC2buffered.tajimasd.allinds.noindels.500.Tajima.D")
tajD.noindels.1k <- read_tsv("all.BNC2buffered.tajimasd.allinds.noindels.1k.Tajima.D")
tajD.noindels.10k <- read_tsv("all.BNC2buffered.tajimasd.allinds.noindels.10k.Tajima.D")



```

# With Indels
All three window sizes of MLF with full gene and buffer
```{r}
ggplot(data = mlf.indels.500, aes(x = BIN_START, y = PI)) +
  geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)

ggplot(data = mlf.indels.1k, aes(x = BIN_START, y = PI)) +
  geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)

ggplot(data = mlf.indels.10k, aes(x = BIN_START, y = PI)) +
  geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)

```

All three window sizes of FLF with full gene and buffer
```{r}
ggplot(data = flf.indels.500, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)

ggplot(data = flf.indels.1k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)

ggplot(data = flf.indels.10k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)
```

All three window sizes of all birds with full gene and buffer
```{r}
ggplot(data = all.indels.500, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)

ggplot(data = all.indels.1k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)

ggplot(data = all.indels.10k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003, col = "red"), size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003, col = "black"), size = 5)
```

Full buffered region and gene, but with indels included
```{r}
ggplot(data = mlf.indels.10k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = flf.indels.10k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

```


# No indels

All window sizes for FLF, full gene and buffer, with exons
```{r}
ggplot(data = flf.noindels.500, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = flf.indels.1k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = flf.indels.10k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  xlim(41584094, 42403202) +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

```

All window sizes for MLF, full gene and buffer, with exons
```{r}
ggplot(data = mlf.noindels.500, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = mlf.noindels.1k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = mlf.noindels.10k, aes(x = BIN_START, y = PI)) +
  geom_line() +
  #geom_point() +
  xlim(41584094, 42403202) +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

```

# Comparisons 

10k window with full buffer
```{r}
ggplot() +
  geom_line(data = all.noindels.10k, aes(x = BIN_START, y = PI)) +
  geom_line(data = mlf.noindels.10k, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.10k, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  xlim(41584094, 42403202) +
  #geom_point() +
  geom_smooth(data = all.noindels.10k, aes(x = BIN_START, y = PI), col = "black") +
  geom_smooth(data = mlf.noindels.10k, aes(x = BIN_START, y = PI), col = "blue") +
  geom_smooth(data = flf.noindels.10k, aes(x = BIN_START, y = PI), col = "red") +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)
```

10k window, zoom into gene
```{r}
ggplot() +
  xlim(41864094, 42133202) +
  geom_line(data = all.noindels.10k, aes(x = BIN_START, y = PI)) +
  geom_smooth(data = all.noindels.10k, aes(x = BIN_START, y = PI), col = "black") +
  geom_line(data = mlf.noindels.10k, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_smooth(data = mlf.noindels.10k, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.10k, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  geom_smooth(data = flf.noindels.10k, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5) +
  theme_classic()
```

10k window, zoom into Fst = 1 region
```{r}
ggplot() +
  xlim(41969101, 42020666) +
  geom_line(data = all.noindels.10k, aes(x = BIN_START, y = PI)) +
  geom_smooth(data = all.noindels.10k, aes(x = BIN_START, y = PI), col = "black") +
  geom_line(data = mlf.noindels.10k, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_smooth(data = mlf.noindels.10k, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.10k, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  geom_smooth(data = flf.noindels.10k, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5) +
  theme_classic()
```

500 window, zoom into Fst = 1 region
```{r}
ggplot() +
  xlim(41972101, 42006666) +
  ylim(0, 0.011) +
  geom_line(data = all.noindels.500, aes(x = BIN_START, y = PI)) +
  geom_smooth(data = all.noindels.500, aes(x = BIN_START, y = PI), col = "black") +
  geom_line(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_smooth(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  geom_smooth(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41988462, xend = 41988463, y = .01, yend = .01), col = "black", size = 5) +
  geom_segment(aes(x = 41988463, xend = 41989101, y = .01, yend = .01), col = "black", size = 3) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .01, yend = .01), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .01, yend = .01), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .01, yend = .01), col = "green", size = 5) +
  theme_classic()
```

Zoom way into region of high Fst
```{r}
ggplot() +
  xlim(41987762, 41990366) +
  ylim(0, 0.011) +
  geom_line(data = all.noindels.500, aes(x = BIN_START, y = PI)) +
  geom_smooth(data = all.noindels.500, aes(x = BIN_START, y = PI), col = "black") +
  geom_line(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_smooth(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  geom_smooth(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41988462, xend = 41988463, y = .01, yend = .01), col = "black", size = 5) +
  geom_segment(aes(x = 41988463, xend = 41989101, y = .01, yend = .01), col = "black", size = 3) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .01, yend = .01), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .01, yend = .01), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .01, yend = .01), col = "green", size = 5) +
  theme_classic()
```

Zoom way into region of high Fst, with very small windows
```{r}
ggplot() +
  xlim(41984462, 41994066) +
  ylim(0, 0.017) +
  geom_line(data = all.noindels.200, aes(x = BIN_START, y = PI)) +
  geom_smooth(data = all.noindels.200, aes(x = BIN_START, y = PI), col = "black") +
  geom_line(data = mlf.noindels.200, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_smooth(data = mlf.noindels.200, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.200, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  geom_smooth(data = flf.noindels.200, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .01, yend = .01), col = "pink", size = 5) +
  geom_segment(aes(x = 41988462, xend = 41988463, y = .01, yend = .01), col = "black", size = 5) +
  geom_segment(aes(x = 41988463, xend = 41989101, y = .01, yend = .01), col = "black", size = 3) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .01, yend = .01), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .01, yend = .01), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .01, yend = .01), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .01, yend = .01), col = "green", size = 5) +
  theme_classic()
```

500 window, full gene but no buffer
```{r}
ggplot() +
  xlim(41864094, 42133202) +
  geom_line(data = all.noindels.500, aes(x = BIN_START, y = PI)) +
  geom_smooth(data = all.noindels.500, aes(x = BIN_START, y = PI), col = "black") +
  geom_line(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_smooth(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  geom_smooth(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  #geom_point() +
  #geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5) +
  theme_classic()
```

500 window with full buffer
```{r}
ggplot() +
  geom_line(data = all.noindels.500, aes(x = BIN_START, y = PI)) +
  geom_line(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue", alpha = 0.3) +
  geom_line(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red", alpha = 0.3) +
  xlim(41584094, 42403202) +
  #geom_point() +
  geom_smooth(data = all.noindels.500, aes(x = BIN_START, y = PI), col = "black") +
  geom_smooth(data = mlf.noindels.500, aes(x = BIN_START, y = PI), col = "blue") +
  geom_smooth(data = flf.noindels.500, aes(x = BIN_START, y = PI), col = "red") +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)
```
# Tajima's D with indels
```{r}
ggplot(data = tajD.indels.100, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = tajD.indels.200, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)


ggplot(data = tajD.indels.1k, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = tajD.indels.10k, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)
```

Zoom into gene
```{r}
ggplot(data = tajD.indels.10k, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  xlim(41750094, 42231202) +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)
```

# Tajima's D with indels removed 

```{r}
ggplot(data = tajD.noindels.100, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = tajD.noindels.500, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)


ggplot(data = tajD.noindels.1k, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)

ggplot(data = tajD.noindels.10k, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)
```
Zoom into gene
```{r}
ggplot(data = tajD.noindels.100, aes(x = BIN_START, y = TajimaD)) +
  geom_line() +
  geom_smooth() +
  #xlim(41750094, 42231202) +
  #xlim(41749462, 42200066) +
  geom_segment(aes(x = 41884094, xend = 42113202, y = .003, yend = .003), col = "pink", size = 5) +
  geom_segment(aes(x = 41989101, xend = 41989666, y = .003, yend = .003), col = "black", size = 5) +
  geom_segment(aes(x = 41884094, xend = 41884204, y = .003, yend = .003), col = "green", size = 5) + 
  geom_segment(aes(x = 41998251, xend = 41998353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42014173, xend = 42014408, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42088387, xend = 42090353, y = .003, yend = .003), col = "green", size = 5) +
  geom_segment(aes(x = 42112542, xend = 42113202, y = .003, yend = .003), col = "green", size = 5)
```